Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-06-25 WRITEUP/ms.tex
edit of sec 5.2

The most massive ($M_{\rm gas}>$10$^7$\,\Msun) cloud corresponds to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
which is identified as a single component at low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a 
low gas mass fraction of $\simeq$\,0.
The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare 
the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) 
in the accreting and quiescent phases of \flower.
The accreting phase of \flower displays a disturbed morphology, whereas the 
quiescent phase displays a disk-like morphology (\Fig{MCC}).
Excluding the structure corresponding to the molecular disk, the 
velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions.
On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
in the quiescent disk-like phase.

The most massive MCC is excluded in the discussion of MCC dynamics in the remainder of this paper
since its dynamics is dominated by large-scale shear.
Considering only the MCCs identified at the highest density threshold, the mass of MCCs is $\simeq10^{6.5}$\,\Msun.
We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) 
have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}). However, the stellar feedback, IGM, merger and accretion histories are not properly modeled in such simulations. That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).

@@

The local sound speed of all molecular complexes identified is typically much smaller than their non-thermal (turbulent) velocities,
as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e., $c_s^2 \ll \sigma_{\rm NT}^2$. In particular, the average Mach number for MCCs identified at the highest density threshold is $\mathcal{M} \simeq6$; this is consistent with the analysis done in \citep{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.

@@

% middle
While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some of them (see \Fig{stellarRatio16}).
% 
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). A large fraction of stellar mass is already assembled in \flower in such MCC, which explains the low total virial parameter seen in the most massive MCC of \flower in this phase, as shown in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability of such MCCs. On the other hand, the  remaining MCCs in this phase are stable, with virial parameter comparable to some of the molecular structures observed in the Milky Way but the former is more massive.

>>>>

The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), 
which is identified as a single component at low $n_{\rm cut}$. This main disk component occupy the top right corner of \Fig{stellarRatio16}, with a 
low gas mass fraction of $f_{\rm gas}\simeq$\,0.
The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare 
the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) 
in the accreting and quiescent phases of \flower.
The accreting phase of \flower displays a disturbed morphology, whereas the 
quiescent phase displays a disk-like morphology (\Fig{MCC}).
Excluding the structure corresponding to the molecular disk, the 
velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions.
On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs
in the quiescent disk-like phase.

The most massive MCC is excluded in the discussion of MCC dynamics in \Sec{diss} of this paper,
since its dynamics is dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}) 
as would be done so for an observational study. % where we would plot everything we identify and try to interpret their nature.

Considering only the MCCs identified at the highest density threshold, the mass of MCCs is $\simeq10^{6.5}$\,\Msun.
We note that similarly massive molecular structures (few times 10$^7$\,\Msun\footnote{See \S{3.1} of \citet{Behrendt16a}.}) 
have been reported in idealized closed-box isolated galaxy simulations done at higher resolution (e.g., a maximum resolution of 3\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}). However, the stellar feedback, IGM, merger and accretion histories are not properly modeled in such simulations. That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off in spite of the limited resolution ($l_{\rm cell}\simeq$\,30\,pc).

@@

The local sound speed of all molecular complexes identified is typically much smaller than their non-thermal (turbulent) velocities,
as non-thermal pressure dominates thermal pressure for dense gas \citep{Pallottini17b}, i.e., $c_s^2 \ll \sigma_{\rm NT}^2$. In particular, the average Mach number for MCCs identified at the highest density threshold is $\bar{\mathcal{M}}\,\simeq6$. This is consistent with the analysis done in \citet{Vallini18a}, that finds a global Mach number of $\mathcal{M} \sim 10$ for \flower.

@@

% middle
While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
% 
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main 
disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower
explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential 
influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with 
virial parameter comparable to some of the molecular structures observed in the Milky Way but the former is more massive.
